On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-30 paper/paper.tex
Added citation to [Andy Gill 2014] paper in the context of capturing lambdas

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda. When these control structures are reified within the EDSL, it is
easier to also reify lambdas, as you can simply apply them to a dummy argument
to access their body (with the dummy value substituted for the argument).
\begin{todo}
  Maybe add brief summary of relationship to lambdas?
\end{todo}

>>>>

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda. When these control structures are reified within the EDSL, it is
easier to also reify lambdas using the dummy argument technique described in~\cite{Gill:2014:DSLSynth}.

% \begin{todo}
%   Maybe add brief summary of relationship to lambdas?
% \end{todo}
